Dynein project log

### 2016-09-23 thesis_stuff/thesis_stuff.tex
Fix rate constants from Winch paper in thesis_stuff.tex.

a: The transition from post-stroke to prestroke in the Winch paper is given by three transitions: the binding of ATP ($k_{+ATP} = 2.2*10^{6} M^{-1}s^{-1}$), dissociation from the microtubule ($k_{-MT} = 460 s^{-1}$) and ATP hydrolysis/taking on the prestroke conformation ($k_{RS} = 180 s^{-1}$). We take the rate-limiting step $k_{RS}$ as our transition rate from bothbound to onebound.\\

b: The transition from prestroke to poststroke in the Winch paper is given by three transitions: binding to the microtubule ($k_{+MT} = 10^4 s^{-1}$), releasing a phosphate from hydrolysis ($k_{-Pi} = 5000 s^{-1}$), the power stroke itself ($k_{PS} = 5000 s^{-1}$) and ADP release ($k_{-ADP} = 1000 s^{-1}$).\\

@@

\section{Todo}
\begin{itemize}
\item Add dt testing figure to thesis\_stuff.tex.
\item Make all figures in thesis\_stuff.tex be dependencies of thesis\_stuff.tex in the Makefile; it should be deducible to a novice how every figure is generated in code.
\item Check out kinetic parameters papers in the Winch model, see how they are aquired
\item Generate a figure explaining how our model simplifies the rate constants in the Winch paper / annual review.
\item Make a figure with PyMol visualizations with and without our model superimposed
\item Calculate Dynein motor efficiency by finding friction work on cargo and energy of ATP.
\end{itemize}
\end{document}

>>>>

a: Sarlah \textit{et al} gives us two different rate constants which could represent the bothbound to onebound transition: motor dissociation from the microtubule ($k_{-MT} = 460 s^{-1}$) and ATP hydrolysis/taking on the prestroke conformation ($k_{RS} = 180 s^{-1}$). We take the rate-limiting step $k_{RS}$ as our transition rate from bothbound to onebound since it is the slower of the two.\\

b: There are several Sarlah \textit{et al} rate constants we could use for the onebound to bothbound rate constant: binding to the microtubule ($k_{+MT} = 10^4 s^{-1}$), releasing a phosphate from hydrolysis ($k_{-Pi} = 5000 s^{-1}$) or the power stroke itself ($k_{PS} = 5000 s^{-1}$). We choose to represent the transition with $k_{-Pi} = 5000 s^{-1}$ because all these rates are fairly similar. We do not want to use the MT-binding rate because it could include both binding kinetics as well as MT-search kinetics, the latter of which we do not want to include in our binding rate.\\

@@

\section{Todo}
\begin{itemize}
\item Add dt testing figure to thesis\_stuff.tex.
\item Make all figures in thesis\_stuff.tex be dependencies of thesis\_stuff.tex in the Makefile; it should be deducible to a novice how every figure is generated in code.
\item Check out kinetic parameters papers in the Winch model, see how they are aquired
\item Generate a figure explaining how our model simplifies the rate constants in the Winch paper / annual review.
\item Make a figure with PyMol visualizations with and without our model superimposed
\item Calculate Dynein motor efficiency by finding friction work on cargo and energy of ATP.
\item Fix generate-stepping-data non-printing bug.
\end{itemize}
\end{document}
